Modelling transient dynamics of granular slopes: MPM \& DEM

### 2016-10-12 paper.tex
Updated with Reviewer 2 comments

\Cref{fig:Normalised_KEx_KEy_Slope} displays the evolution of kinetic energy 
in the translational ($E_x$ and $E_y$) degrees of freedom. $E_x$ decays similar 
to the total energy dissipation, but $E_y$ increases and passes through a peak 
before decaying rapidly to a negligible level. The transient is best 
observed for $E_y$, which has significant values only for $t< t_1$. This energy 
represents the proportion of kinetic energy transferred to the $y$ component of 
the velocity field  due to the destabilisation of the slope and collapse of 
grains in the cavity behind the slope. Higher proportion of vertical 
acceleration $E_{ky}/E_0$ is observed for lower values of input energy $E_0$. 
This means that, at lower input energies a larger fraction of the energy is 
consumed in the destabilisation process. Whereas at a higher input energies, 
most of the energy is dissipated in the spreading phase. For this reason, the 
total duration $t_1$ of this destabilisation phase is nearly the same in 
both regimes and its value is controlled by gravity rather than the input 
energy. The height of the slope being of the order of $80 \ d$, the total 
free-fall time for a particle located at this height is $\simeq 12 \ 
(d/g)^{0.5}$, which is of the same order as $t_1$. DEM simulations show that 
the contribution of the rotational energy during the transient stage and the 
spreading stage is negligible.

@@

  \item Two regimes with different values of the exponents: 
    a low-energy regime and a high-energy regime are observed.

@@

\section*{Acknowledgements}
The authors would like to thank Professor F. Radjai, LMGC, Montpellier, France for stimulating discussions regarding this work. The author would like to thank the Cambridge Commonwealth and Overseas Trust for the financial support to the first author to pursue this research.

>>>>

\Cref{fig:Normalised_KEx_KEy_Slope} displays the evolution of kinetic energy 
in the translational ($E_x$ and $E_y$) degrees of freedom. $E_x$ decays similar 
to the total energy dissipation, but $E_y$ increases and passes through a peak 
before decaying rapidly to a negligible level. The transient is best 
observed for $E_y$, which has significant values only for $t< t_1$. This energy 
represents the proportion of kinetic energy transferred to the $y$ component of 
the velocity field  due to the destabilisation of the slope and collapse of 
grains in the cavity behind the slope. Higher proportion of vertical 
acceleration $E_{ky}/E_0$ is observed for lower values of input energy $E_0$. 
This means that, at lower input energies a larger fraction of the energy is 
consumed in the destabilisation process, which results in osciallation in the
kinetic energy. Whereas at a higher input energies, most of the energy is
dissipated in the spreading phase. For this reason, the total duration $t_1$
of this destabilisation phase is nearly the same in both regimes and its
value is controlled by gravity rather than the input energy. The height of
the slope being of the order of $80 \ d$, the total free-fall time for a
particle located at this height is $\simeq 12 \ (d/g)^{0.5}$, which is of the
same order as $t_1$. DEM simulations show that the contribution of the
rotational energy during the transient stage and the spreading stage is
negligible.

@@

  \item Two regimes with different values of the exponents are observed: 
    a low-energy and a high-energy regime.

@@

\section*{Acknowledgements}
The author would like to thank the Cambridge Commonwealth and Overseas Trust for the financial support to the first author to pursue this research.
